The Power of Two Random Choices

### 2014-03-25 presentation/presentation.tex
some more minor fixes

\begin{description}
\item[\alert{Sequential:}] The balls arrive one after another, one at each time step $t$.
\item[\alert{Infinite:}] Ball placements and deletions are given for an infinite time span.
\item[\alert{Dynamic:}] Balls do not stay in the bins forever.
\begin{itemize}
\item An oblivious adversary provides a sequence $\sigma = \sigma_1 \sigma_2 \dots$, where $\sigma_t = (d_t, a_t)$.
\item $d_t$/$a_t$: ball to delete/add at time step t. \\
\item $\sigma$ is fixed in advance.
\end{itemize}
\end{description}
\end{frame}

\begin{frame}
\frametitle{Proof of either Greedy or Always-go-left}
I suggest to present the Greedy proof:
\begin{itemize}
\item Both proofs have the same structure, but Always-go-left is a lot more technical
\item For Always-go-left, d-ary Fibonacci trees and a generalized golden ratio need to be introduced
\item complete d-ary trees are easier to think and reason about (number of nodes/leaves, the inductive argument used)
\end{itemize}
\end{frame}

@@

%\againframe{references}
%todo: why so few references shown?
\begin{frame}[allowframebreaks, label=references]
\frametitle<presentation>{References}    
\bibliographystyle{acm}
\nocite{*}
\setbeamertemplate{bibliography item}[text]
\bibliography{../sources}
\end{frame}

>>>>

\begin{description}
\item[\alert{Sequential:}] The balls arrive one after another, one at each time step~$t$.
\item[\alert{Infinite:}] Ball placements and deletions are given for an infinite time span.
\item[\alert{Dynamic:}] Balls do not stay in the bins forever.
\begin{itemize}
\item An oblivious adversary provides a sequence $\sigma = \sigma_1 \sigma_2 \dots$, where $\sigma_t = (d_t, a_t)$.
\item $d_t$/$a_t$: ball to delete/add at time step t. \\
\item $\sigma$ is fixed in advance.
\end{itemize}
\end{description}
\end{frame}

\begin{frame}
\frametitle{Proof of either Greedy or Always-go-left}
I suggest to present the Greedy proof:
\begin{itemize}
\item Both proofs have the same structure, but Always-go-left is a lot more technical.
\item For Always-go-left, d-ary Fibonacci trees and a generalized golden ratio need to be introduced.
\item Complete d-ary trees are easier to think and reason about (number of nodes/leaves, the inductive argument used).
\end{itemize}
\todo{The following slides are preliminary.}
\end{frame}

@@

%\againframe{references}
%todo: why so few references shown?
\begin{frame}[allowframebreaks, label=references]
\frametitle<presentation>{References}    
\bibliographystyle{acm}
\nocite{ABKU99}
%\nocite{RS98}
\nocite{VOC03}
\setbeamertemplate{bibliography item}[text]
\bibliography{../sources}
\end{frame}
